Abstract Binding Trees

### 2015-10-30 paper.tex
Move footnote; formatting; notation

\begin{remark}
  A presheaf $P$ with a substitution monoidal structure $\Pair{\nu}{\varsigma}$
  also forms a \emph{relative monad} on the functor
  $\Of{V}{\widehat{\HypCat}^\Sorts}$ of variables.\footnote{Relative monads are
    skew-monoids in the skew-monoidal structure induced by a functor category
    $\mathbf{C}^\mathbf{J}$ \cite{altenkirch-chapman-uustalu:2015}. However,
    relative monads can also be understood without reference to monoids by
    viewing them as a generalization of \emph{extension systems} or
    \emph{Kleisli structures}. This latter presentation of monads, popular in
    computer science and logic, does not involve iteration of the monad
    functor.} Consequently, the monoid multiplication $\odot$ can be replaced
  with an extension operation:
  \[
    \begin{tikzcd}[ampersand replacement = \&]
      {\IMode{P(\,=\,)^{V(\,-\,)}}} \arrow[r, "(\,-\,)^{P}"]
      \& {\IMode{P(\,=\,)^{P(\,-\,)}}}
    \end{tikzcd}
  \]
\end{remark}

>>>>

\begin{remark}
  A presheaf $P$ with a substitution monoidal structure $\Pair{\nu}{\varsigma}$
  also forms a \emph{relative monad}\footnote{Relative monads are skew-monoids
    in the skew-monoidal structure induced by a functor category
    $\mathbf{C}^\mathbf{J}$ \cite{altenkirch-chapman-uustalu:2015}. However,
    relative monads can also be understood without reference to monoids by
    viewing them as a generalization of \emph{extension systems} or
    \emph{Kleisli structures}. This latter presentation of monads, popular in
    computer science and logic, does not involve iteration of the monad
    functor.} on the functor $\Of{V}{\widehat{\HypCat}^\Sorts}$ of variables.
  Consequently, the monoid multiplication $\odot$ can be replaced with an
  extension operation:
  \[
    \begin{tikzcd}[ampersand replacement = \&, sep = huge]
      {\IMode{P(\,=\,)^{V(\,-\,)}}} \arrow[r, "(\,-\,)^{\circledast}"]
      \& {\IMode{P(\,=\,)^{P(\,-\,)}}}
    \end{tikzcd}
  \]
\end{remark}
